TBD

### 2021-03-18 outputs/paper/paper.Rmd
bib updates

@@

```{r loaddata, echo=FALSE, warning=FALSE, message=FALSE}
library(here) # locate the file path
data<- load(here::here("inputs/data/deepfake.RData"))
EDA<- dat%>%
        select(treat, response_wave_ID, exp_1_prompt, meta_OS, age_65, educ, PID, crt, gender, age, polknow, internet_usage, ambivalent_sexism, post_favor_Warren,believed_true)

@@

## Multiple Linear Regression
We are using RStudio to run the multiple linear regression model. The following reasons explain why we decide to choose multiple linear regression:
* It account for all of the potentially important factors in one model
* It leads to a more precise understanding of the relationship between dependent variables and independent variables
* It is able to identify outliers or anomalies in the dataset.

@@

R squared : 
R-squared  is a measure of the goodness of fit of the model. A larger R-squared  indicates a closer fit of the model to the data. It is used as an optimality criterion in parameter selection and model selection.
P-value:
P-value is used to describe the occurrence possibility of the extreme outcome when the null hypothesis is true. If the p-value is small, it means that the probability of occurrence of the null hypothesis to be true is very small. And if it does occur, we have a reason to reject the null hypothesis. In short, the smaller the p-value, the more significant the result. Usually the threshold for significant p value is set to 0.05.
Regression coefficient:
The sign of the regression coefficient describes whether there is a positive or negative correlation between each feature variable and the dependent variable (Warren affective score). A positive coefficient means that as the value of the independent variable increases, the average value of the affective score also tends to increase. A negative coefficient indicates that as the independent variable increases, the affective score tends to decrease.

@@

## Appendix A {#appendixA}
```{r missing, fig.cap="Missing value Visualization ", echo=FALSE, fig.width=10, fig.height=10}

library("VIM")
aggr(dat,prop=FALSE,numbers=TRUE)

```{r figure1,fig.cap="Scale-Location plot", echo=FALSE, fig.width=10, fig.height=10}
plot(model,which = 3)
```

```{r figure2,fig.cap="Normal QQ-plot", echo=FALSE, fig.width=10, fig.height=10}
plot(model,which = 2)
```

```{r figure3,fig.cap="Residual versus Leverage plot", echo=FALSE, fig.width=10, fig.height=10}
plot(model,which = 5)
```

>>>>

We replicate this paper using R statistical programming language [@citeR]. In particular, we use packages `tidyverse` [@citetidyverse],  `here` [@citehere], `ggpubr` [@citeggpubr] to manipulate data and packages, `kableExtra` [@citekableExtra] to generate tables, and `ggplot2` [@citeggplot], `ggthemes` [@citeggthemes] to adjust diagrams themes.

## Intervention

@@

```{r loaddata, echo=FALSE, warning=FALSE, message=FALSE}
library(here) # locate the file path
data<- load(here::here("inputs/data/deepfake.RData"))

EDA<- dat%>%
        select(treat, response_wave_ID, exp_1_prompt, meta_OS, age_65, educ, PID, crt, gender, age, polknow, internet_usage, ambivalent_sexism, post_favor_Warren,believed_true)

@@

## Multiple Linear Regression
We are using RStudio to run the multiple linear regression model. The following reasons explain why we decide to choose multiple linear regression:

* It account for all of the potentially important factors in one model
* It leads to a more precise understanding of the relationship between dependent variables and independent variables
* It is able to identify outliers or anomalies in the dataset.

@@

R squared :

R-squared  is a measure of the goodness of fit of the model. A larger R-squared  indicates a closer fit of the model to the data. It is used as an optimality criterion in parameter selection and model selection.

P-value:

P-value is used to describe the occurrence possibility of the extreme outcome when the null hypothesis is true. If the p-value is small, it means that the probability of occurrence of the null hypothesis to be true is very small. And if it does occur, we have a reason to reject the null hypothesis. In short, the smaller the p-value, the more significant the result. Usually the threshold for significant p value is set to 0.05.

Regression coefficient:

The sign of the regression coefficient describes whether there is a positive or negative correlation between each feature variable and the dependent variable (Warren affective score). A positive coefficient means that as the value of the independent variable increases, the average value of the affective score also tends to increase. A negative coefficient indicates that as the independent variable increases, the affective score tends to decrease.

@@

## Appendix A {#appendixA}
```{r missing, fig.cap="Missing value Visualization ", echo=FALSE, warning =FALSE, out.width = "50%", fig.width=10, fig.height=10}

# library("VIM")
# aggr(dat,prop=FALSE,numbers=TRUE)

# include the plot from script
# library(here)
knitr::include_graphics(here::here("outputs/paper/Missing values.png"))
```

```{r figure1,fig.cap="Scale-Location plot", echo=FALSE, warning =FALSE, fig.width=10, fig.height=10}
plot(model,which = 3)
```

```{r figure2,fig.cap="Normal QQ-plot", echo=FALSE, warning =FALSE, fig.width=10, fig.height=10}
plot(model,which = 2)
```

```{r figure3,fig.cap="Residual versus Leverage plot", echo=FALSE, warning =FALSE, fig.width=10, fig.height=10}
plot(model,which = 5)
```
